FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-23 paper.tex
ganesh note: FPtracker + GPUFPX
ieee 754 quiet nan, retrospective analysis

@@

>>>>

\subsubsection{TODO good quote, try to work this in}

From IEEE 754. Section 6.2 here: \url{http://www.dsc.ufcg.edu.br/~cnum/modulos/Modulo2/IEEE754\_2008.pdf}:

\begin{quote}
  Quiet NaNs should, by means left to the implementer’s discretion, afford
  retrospective diagnostic information inherited from invalid or unavailable
  data and results.
\end{quote}

Found via \url{https://anniecherkaev.com/the-secret-life-of-nan}

TODO what other tools are there for retrospective diagnosis?

@@

%% Ganesh
% 3) These are conceptually usable together (Julia calling GPU kernels below).
% The usage is simple: Start the Julia application that calls a GPU kernel under
% LD_PRELOAD as with GPU-FPX launch. When this launch transfers control to a GPU
% kernel, the GPU-FPX instrumentation starts notifying the exceptions on the
% console of the CPU. When the GPU launch returns, the exceptions go in the
% return call path of the Julia execution. Ashton and Xinyi plz validate this
% scenario
